---
title: "TextMining"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Unnest_token functions

```{r}
text <- c("Because I could not stop for Death -",
          "He kindly stopped for me -",
          "The Carriage held but just Ourselves -",
          "and Immortality")

library(dplyr)
text_df <- data_frame(line = 1:4, text = text)

library(tidytext)

text_df %>%
  unnest_tokens(word, text)

```

#Example
```{r}
library(janeaustenr)
library(dplyr)
library(stringr)

original_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]",
                                                 ignore_case = TRUE)))) %>%
  ungroup()

library(tidytext)
tidy_books <- original_books %>%
  unnest_tokens(word, text)

tidy_books

#Removing stop words
data(stop_words)
tidy_books <- tidy_books %>%
  anti_join(stop_words)

#Count words
tidy_books %>%
  count(word, sort = TRUE) 

#Graphics
library(ggplot2)
library(RColorBrewer)
colors <- brewer.pal(4, "BuPu")
pal <- colorRampPalette(colors)
pal(30)

tidy_books %>%
  count(word, sort = TRUE) %>%
  filter(n > 600) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x=word, y=n,fill=word)) +
  geom_bar(stat="identity") +
  scale_fill_brewer(palette = pal(13))+
  coord_flip()

```

```{r}
library(gutenbergr)

#HG wells books
hgwells <- gutenberg_download(c(35, 36, 5230, 159))

tidy_hgwells <- hgwells %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

tidy_hgwells %>%
  count(word, sort = TRUE)
```

```{r}
#Bronte books
bronte <- gutenberg_download(c(1260, 768, 969, 9182, 767))

tidy_bronte <- bronte %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)
```
```{r}
#Joining word count
library(tidyr)

frequency <- bind_rows(mutate(tidy_bronte, author = "Brontë Sisters"),
                       mutate(tidy_hgwells, author = "H.G. Wells"), 
                       mutate(tidy_books, author = "Jane Austen")) %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(author, word) %>%
  group_by(author) %>%
  mutate(proportion = n / sum(n)) %>% 
  select(-n) %>% 
  spread(author, proportion) %>% 
  gather(author, proportion, `Brontë Sisters`:`H.G. Wells`)
```

```{r}
#Frequence graphic
library(ggplot2)
library(scales)
ggplot(frequency, aes(x = proportion, y = `Jane Austen`, color = abs(`Jane Austen` - proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), low = "darkslategray4", high = "gray75") +
  facet_wrap(~author, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "Jane Austen", x = NULL)
```

##Correlation test

```{r}
cor.test(data = frequency[frequency$author == "Brontë Sisters",],
         ~ proportion + `Jane Austen`)

cor.test(data = frequency[frequency$author == "H.G. Wells",],
         ~ proportion + `Jane Austen`)
```

#Sentiment analysis
```{r}
library(tidytext)

#Get lexicon
get_sentiments("afinn")

library(janeaustenr)
library(dplyr)
library(stringr)

tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]", 
                                                 ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)
```

```{r}
#Joy sentiment
nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)
```

```{r}
library(tidyr)

jane_austen_sentiment <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>% 
  count(book, index = linenumber %/% 80, sentiment)%>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)

library(ggplot2)

ggplot(jane_austen_sentiment, aes(index, sentiment, fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x")

```

```{r}
pride_prejudice <- tidy_books %>% 
  filter(book == "Pride & Prejudice")


afinn <- pride_prejudice %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(score)) %>% 
  mutate(method = "AFINN")

bing_and_nrc <- bind_rows(pride_prejudice %>% 
                            inner_join(get_sentiments("bing")) %>%
                            mutate(method = "Bing et al."),
                          pride_prejudice %>% 
                            inner_join(get_sentiments("nrc") %>% 
                                         filter(sentiment %in% c("positive", 
                                                                 "negative"))) %>%
                            mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)

bind_rows(afinn, 
          bing_and_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")
```

##Most common positive and negative words

```{r}
bing_word_counts <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts
```

```{r}
bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip()
```

```{r}
#Custom stop words settings
custom_stop_words <- bind_rows(data_frame(word = c("miss"), 
                                          lexicon = c("custom")), 
                               stop_words)

custom_stop_words
```

```{r}
library(wordcloud)

tidy_books %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```

```{r}
library(reshape2)

test=tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0)%>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)
```

```{r}
PandP_sentences <- data_frame(text = prideprejudice) %>% 
  unnest_tokens(sentence, text, token = "sentences")

PandP_sentences$sentence[2]
```

```{r}
austen_chapters <- austen_books() %>%
  group_by(book) %>%
  unnest_tokens(chapter, text, token = "regex", 
                pattern = "Chapter|CHAPTER [\\dIVXLC]") %>%
  ungroup()

austen_chapters %>% 
  group_by(book) %>% 
  summarise(chapters = n())
```

```{r}
bingnegative <- get_sentiments("bing") %>% 
  filter(sentiment == "negative")

wordcounts <- tidy_books %>%
  group_by(book, chapter) %>%
  summarize(words = n())

tidy_books %>%
  semi_join(bingnegative) %>%
  group_by(book, chapter) %>%
  summarize(negativewords = n()) %>%
  left_join(wordcounts, by = c("book", "chapter")) %>%
  mutate(ratio = negativewords/words) %>%
  filter(chapter != 0) %>%
  top_n(1) %>%
  ungroup()
```

#Analyzing word and document frequency: tf-idf

##Term frequency
```{r}
library(dplyr)
library(janeaustenr)
library(tidytext)

book_words <- austen_books() %>%
  unnest_tokens(word, text) %>%
  count(book, word, sort = TRUE) %>%
  ungroup()

total_words <- book_words %>% 
  group_by(book) %>% 
  summarize(total = sum(n))

book_words <- left_join(book_words, total_words)

library(ggplot2)

ggplot(book_words, aes(n/total, fill = book)) +
  geom_histogram(show.legend = FALSE) +
  xlim(NA, 0.0009) +
  facet_wrap(~book, ncol = 2, scales = "free_y")
```
##Zipf law

```{r}
freq_by_rank <- book_words %>% 
  group_by(book) %>% 
  mutate(rank = row_number(), 
         `term frequency` = n/total)

freq_by_rank %>% 
  ggplot(aes(rank, `term frequency`, color = book)) + 
  geom_line(size = 1.1, alpha = 0.8, show.legend = FALSE) + 
  scale_x_log10() +
  scale_y_log10()

```

```{r}
#Power law

rank_subset <- freq_by_rank %>% 
  filter(rank < 500,
         rank > 10)

lm(log10(`term frequency`) ~ log10(rank), data = rank_subset)

freq_by_rank %>% 
  ggplot(aes(rank, `term frequency`, color = book)) + 
  geom_abline(intercept = -0.62, slope = -1.1, color = "gray50", linetype = 2) +
  geom_line(size = 1.1, alpha = 0.8, show.legend = FALSE) + 
  scale_x_log10() +
  scale_y_log10()

#Smaller term frequency for rare term compared to power law
```

##tf-idf calculation

```{r}
#Top terms with tf-idf
book_words <- book_words %>%
  bind_tf_idf(word, book, n)

book_words %>%
  select(-total) %>%
  arrange(desc(tf_idf))
```

```{r,fig.height=7}
book_words %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  group_by(book) %>% 
  top_n(15) %>% 
  ungroup %>%
  ggplot(aes(word, tf_idf, fill = book)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~book, ncol = 2, scales = "free") +
  coord_flip()
```

#Example of physics text
```{r}
library(gutenbergr)
physics <- gutenberg_download(c(37729, 14725, 13476, 5001), 
                              meta_fields = "author")
```

```{r}
physics_words <- physics %>%
  unnest_tokens(word, text) %>%
  count(author, word, sort = TRUE) %>%
  ungroup()

physics_words
```

```{r}
plot_physics <- physics_words %>%
  bind_tf_idf(word, author, n) %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  mutate(author = factor(author, levels = c("Galilei, Galileo",
                                            "Huygens, Christiaan", 
                                            "Tesla, Nikola",
                                            "Einstein, Albert")))

plot_physics %>% 
  group_by(author) %>% 
  top_n(15, tf_idf) %>% 
  ungroup() %>%
  mutate(word = reorder(word, tf_idf)) %>%
  ggplot(aes(word, tf_idf, fill = author)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~author, ncol = 2, scales = "free") +
  coord_flip()
```

```{r}
#Explorating strange terms 
library(stringr)

physics %>% 
  filter(str_detect(text, "eq\\.")) %>% 
  select(text)
```

```{r}
mystopwords <- data_frame(word = c("eq", "co", "rc", "ac", "ak", "bn", 
                                   "fig", "file", "cg", "cb", "cm"))
physics_words <- anti_join(physics_words, mystopwords, by = "word")
plot_physics <- physics_words %>%
  bind_tf_idf(word, author, n) %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  group_by(author) %>% 
  top_n(15, tf_idf) %>%
  ungroup %>%
  mutate(author = factor(author, levels = c("Galilei, Galileo",
                                            "Huygens, Christiaan",
                                            "Tesla, Nikola",
                                            "Einstein, Albert")))

ggplot(plot_physics, aes(word, tf_idf, fill = author)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~author, ncol = 2, scales = "free")+
  coord_flip()

```

#Relationship between words

```{r}
library(dplyr)
library(tidytext)
library(janeaustenr)

austen_bigrams <- austen_books() %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)

austen_bigrams
```

```{r}
#Filtering stop words in bigram
austen_bigrams %>%
  count(bigram, sort = TRUE)

library(tidyr)

bigrams_separated <- austen_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)

# new bigram counts:
bigram_counts <- bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)

bigram_counts
```

##Trigrams

```{r}
austen_books() %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3) %>%
  separate(trigram, c("word1", "word2", "word3"), sep = " ") %>%
  filter(!word1 %in% stop_words$word,
         !word2 %in% stop_words$word,
         !word3 %in% stop_words$word) %>%
  count(word1, word2, word3, sort = TRUE)
```

```{r}
#Analyzing bigrams
bigrams_filtered %>%
  filter(word2 == "street") %>%
  count(book, word1, sort = TRUE)

bigrams_united <- bigrams_filtered %>%
  unite(bigram, word1, word2, sep = " ")

bigram_tf_idf <- bigrams_united %>%
  count(book, bigram) %>%
  bind_tf_idf(bigram, book, n) %>%
  arrange(desc(tf_idf))

bigram_tf_idf
```

##Bigrams and sentiment analysis

```{r}
bigrams_separated %>%
  filter(word1 == "not") %>%
  count(word1, word2, sort = TRUE)

AFINN <- get_sentiments("afinn")

not_words <- bigrams_separated %>%
  filter(word1 == "not") %>%
  inner_join(AFINN, by = c(word2 = "word")) %>%
  count(word2, score, sort = TRUE) %>%
  ungroup()

not_words

```

```{r}
not_words %>%
  mutate(contribution = n * score) %>%
  arrange(desc(abs(contribution))) %>%
  head(20) %>%
  mutate(word2 = reorder(word2, contribution)) %>%
  ggplot(aes(word2, n * score, fill = n * score > 0)) +
  geom_col(show.legend = FALSE) +
  xlab("Words preceded by \"not\"") +
  ylab("Sentiment score * number of occurrences") +
  coord_flip()
```

```{r}
negation_words <- c("not", "no", "never", "without")

negated_words <- bigrams_separated %>%
  filter(word1 %in% negation_words) %>%
  inner_join(AFINN, by = c(word2 = "word")) %>%
  count(word1, word2, score, sort = TRUE) %>%
  ungroup()

```

##Visualizing network of bigram with ggraph

```{r}
library(igraph)
# original counts
bigram_counts
```

```{r}
# filter for only relatively common combinations
bigram_graph <- bigram_counts %>%
  filter(n > 20) %>%
  graph_from_data_frame()

bigram_graph

library(ggraph)
set.seed(2017)

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)
```

##Counting and correlating among sections

```{r}
austen_section_words <- austen_books() %>%
  filter(book == "Pride & Prejudice") %>%
  mutate(section = row_number() %/% 10) %>%
  filter(section > 0) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word)

austen_section_words

library(widyr)

# count words co-occuring within sections
word_pairs <- austen_section_words %>%
  pairwise_count(word, section, sort = TRUE)

word_pairs

word_pairs %>%
  filter(item1 == "darcy")
```

##Pairwise correlation

```{r}
word_cors <- austen_section_words %>%
  group_by(word) %>%
  filter(n() >= 20) %>%
  pairwise_cor(word, section, sort = TRUE)

word_cors

word_cors %>%
  filter(item1 == "pounds")

word_cors %>%
  filter(item1 %in% c("elizabeth", "pounds", "married", "pride")) %>%
  group_by(item1) %>%
  top_n(6) %>%
  ungroup() %>%
  mutate(item2 = reorder(item2, correlation)) %>%
  ggplot(aes(item2, correlation)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ item1, scales = "free") +
  coord_flip()
```

#Converting to and from non-tidy formats

##Tidying DocumentTermMatrix objects
```{r}
library(tm)

data("AssociatedPress", package = "topicmodels")
AssociatedPress

terms <- Terms(AssociatedPress)
head(terms)
```

```{r}
#tidy DTM
library(dplyr)
library(tidytext)

ap_td <- tidy(AssociatedPress)
ap_td

#Sentiment analysis
ap_sentiments <- ap_td %>%
  inner_join(get_sentiments("bing"), by = c(term = "word"))

ap_sentiments

ap_sentiments %>%
  count(sentiment, term, wt = count) %>%
  ungroup() %>%
  filter(n >= 200) %>%
  mutate(n = ifelse(sentiment == "negative", -n, n)) %>%
  mutate(term = reorder(term, n)) %>%
  ggplot(aes(term, n, fill = sentiment)) +
  geom_bar(stat = "identity") +
  ylab("Contribution to sentiment") +
  coord_flip()
```

```{r}
#DFM (Document Feature Matrix)
data("data_corpus_inaugural", package = "quanteda")
inaug_dfm <- quanteda::dfm(data_corpus_inaugural, verbose = FALSE)

inaug_td <- tidy(inaug_dfm)

inaug_tf_idf <- inaug_td %>%
  bind_tf_idf(term, document, count) %>%
  arrange(desc(tf_idf))

inaug_tf_idf

library(tidyr)

year_term_counts <- inaug_td %>%
  extract(document, "year", "(\\d+)", convert = TRUE) %>%
  complete(year, term, fill = list(count = 0)) %>%
  group_by(year) %>%
  mutate(year_total = sum(count))

year_term_counts %>%
  filter(term %in% c("god", "america", "foreign", "union", "constitution", "freedom")) %>%
  ggplot(aes(year, count / year_total)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~ term, scales = "free_y") +
  scale_y_continuous(labels = scales::percent_format()) +
  ylab("% frequency of word in inaugural address")
```

##Casting tidy text data into a matrix
```{r}
library(tidytext)
ap_td %>%
  cast_dtm(document, term, count)

ap_td %>%
  cast_dfm(document, term, count)
```

```{r}
#Creating a sparse matrix
library(Matrix)

# cast into a Matrix object
m <- ap_td %>%
  cast_sparse(document, term, count)

class(m)
```

```{r}
#Example as creating dtm from books
library(janeaustenr)
library(dplyr)

austen_dtm <- austen_books() %>%
  unnest_tokens(word, text) %>%
  count(book, word) %>%
  cast_dtm(book, word, n)

austen_dtm
```

##Tidying corpus objects with metadata
```{r}
library(tm)
data("acq")
acq[[1]]

#tidy including metadata
acq_td <- tidy(acq)
acq_td
```

```{r}
#Tokenization
acq_tokens <- acq_td %>%
  select(-places) %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words, by = "word")

# most common words
acq_tokens %>%
  count(word, sort = TRUE)

acq_tokens %>%
  count(id, word) %>%
  bind_tf_idf(word, id, n) %>%
  arrange(desc(tf_idf))
```

```{r,eval=FALSE}
#Example download financial resources
library(tm.plugin.webmining)
library(purrr)

company <- c("Microsoft", "Apple", "Google", "Amazon", "Facebook",
             "Twitter", "IBM", "Yahoo", "Netflix")
symbol <- c("MSFT", "AAPL", "GOOG", "AMZN", "FB", "TWTR", "IBM", "YHOO", "NFLX")

download_articles <- function(symbol) {
  tm.plugin.webmining::WebCorpus(tm.plugin.webmining::YahooFinanceSource(paste0("NASDAQ:", symbol)))
}

stock_articles <- data_frame(company = company,
                             symbol = symbol) %>%
  mutate(corpus = purrr::map(symbol, download_articles))

#Tokenization
library(tidyr)
stock_tokens <- stock_articles %>%
  unnest(map(corpus, tidy))%>%
  unnest_tokens(word, text)

stock_tokens
```

```{r}
library(stringr)

stock_tf_idf <- stock_tokens %>%
  count(company, word) %>%
  filter(!str_detect(word, "\\d+")) %>%
  bind_tf_idf(word, company, n) %>%
  arrange(-tf_idf)
```

#Topic modeling

```{r}
library(topicmodels)

data("AssociatedPress")
AssociatedPress

ap_lda <- LDA(AssociatedPress, k = 2, control = list(seed = 1234))
ap_lda
```

```{r}
#Extracting beta parameters
library(tidytext)

ap_topics <- tidy(ap_lda, matrix = "beta")
ap_topics

#Representing top beta for each topic
library(ggplot2)
library(dplyr)

ap_top_terms <- ap_topics %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

ap_top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()
```

```{r}
#Calculating the log ratio of topics
library(tidyr)

beta_spread <- ap_topics %>%
  mutate(topic = paste0("topic", topic)) %>%
  spread(topic, beta) %>%
  filter(topic1 > .001 | topic2 > .001) %>%
  mutate(log_ratio = log2(topic2 / topic1)) %>% 
  mutate(abs_log=abs(log_ratio)) %>% 
  top_n(20,abs_log) %>% 
  mutate(term=reorder(term,log_ratio))

beta_spread

ggplot(data=beta_spread,aes(term,log_ratio))+
  geom_col(show.legend=FALSE)+
  coord_flip()
```

##Document topics probabilities

```{r}
ap_documents <- tidy(ap_lda, matrix = "gamma")
ap_documents
```

##Concrete example

```{r}
titles <- c("Twenty Thousand Leagues under the Sea", "The War of the Worlds",
            "Pride and Prejudice", "Great Expectations")

library(gutenbergr)

books <- gutenberg_works(title %in% titles) %>%
  gutenberg_download(meta_fields = "title")


```

```{r}
library(stringr)

# divide into documents, each representing one chapter
by_chapter <- books %>%
  group_by(title) %>%
  mutate(chapter = cumsum(str_detect(text, regex("^chapter ", ignore_case = TRUE)))) %>%
  ungroup() %>%
  filter(chapter > 0) %>%
  unite(document, title, chapter)

# split into words
by_chapter_word <- by_chapter %>%
  unnest_tokens(word, text)

# find document-word counts
word_counts <- by_chapter_word %>%
  anti_join(stop_words) %>%
  count(document, word, sort = TRUE) %>%
  ungroup()

word_counts

```

```{r}
#LDA modeling
chapters_dtm <- word_counts %>%
  cast_dtm(document, word, n)

chapters_dtm

chapters_lda <- LDA(chapters_dtm, k = 4, control = list(seed = 1234))
chapters_lda

chapter_topics <- tidy(chapters_lda, matrix = "beta")

top_terms <- chapter_topics %>%
  group_by(topic) %>%
  top_n(5, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

library(ggplot2)

top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()
```

##Per-document classification
```{r}
chapters_gamma <- tidy(chapters_lda, matrix = "gamma")
chapters_gamma

chapters_gamma <- chapters_gamma %>%
  separate(document, c("title", "chapter"), sep = "_", convert = TRUE)

chapters_gamma
```

```{r}
chapters_gamma %>%
  mutate(title = reorder(title, gamma * topic)) %>%
  ggplot(aes(factor(topic), gamma)) +
  geom_boxplot() +
  facet_wrap(~ title)

```

```{r}
chapter_classifications <- chapters_gamma %>%
  group_by(title, chapter) %>%
  top_n(1, gamma) %>%
  ungroup()

chapter_classifications
```

```{r}
#Compare consensus topic for each book
book_topics <- chapter_classifications %>%
  count(title, topic) %>%
  group_by(title) %>%
  top_n(1, n) %>%
  ungroup() %>%
  transmute(consensus = title, topic)

chapter_classifications %>%
  inner_join(book_topics, by = "topic") %>%
  filter(title != consensus)
```

##By word assignment
```{r}
assignments <- augment(chapters_lda, data = chapters_dtm)
assignments

assignments <- assignments %>%
  separate(document, c("title", "chapter"), sep = "_", convert = TRUE) %>%
  inner_join(book_topics, by = c(".topic" = "topic"))

assignments
```

```{r}
#Visualizing consensus
library(scales)
assignments %>%
  count(title, consensus, wt = count) %>%
  group_by(title) %>%
  mutate(percent = n / sum(n)) %>%
  ggplot(aes(consensus, title, fill = percent)) +
  geom_tile() +
  scale_fill_gradient2(high = "red", label = percent_format()) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        panel.grid = element_blank()) +
  labs(x = "Book words were assigned to",
       y = "Book words came from",
       fill = "% of assignments")
```

```{r}
wrong_words <- assignments %>%
  filter(title != consensus)

wrong_words
```

##Alternatives LDA implementation
```{r}
library(mallet)

# create a vector with one string per chapter
collapsed <- by_chapter_word %>%
  anti_join(stop_words, by = "word") %>%
  mutate(word = str_replace(word, "'", "")) %>%
  group_by(document) %>%
  summarize(text = paste(word, collapse = " "))

# create an empty file of "stopwords"
file.create(empty_file <- tempfile())
docs <- mallet.import(collapsed$document, collapsed$text, empty_file)

mallet_model <- MalletLDA(num.topics = 4)
mallet_model$loadDocuments(docs)
mallet_model$train(100)
```

```{r}
tidy(mallet_model)

# document-topic pairs
tidy(mallet_model, matrix = "gamma")

# column needs to be named "term" for "augment"
term_counts <- rename(word_counts, term = word)
augment(mallet_model, term_counts)
```

#Case study: mining NASA metadata

```{r}
library(jsonlite)
metadata <- fromJSON("https://data.nasa.gov/data.json")
names(metadata$dataset)
```

```{r}
#Tidy and wrangling the data
library(dplyr)

nasa_title <- data_frame(id = metadata$dataset$`_id`$`$oid`, 
                         title = metadata$dataset$title)
nasa_title

library(tidyr)

nasa_keyword <- data_frame(id = metadata$dataset$`_id`$`$oid`, 
                           keyword = metadata$dataset$keyword) %>%
  #Using nest because it is a list-column
  unnest(keyword)

nasa_desc <- data_frame(id = metadata$dataset$`_id`$`$oid`, 
                        desc = metadata$dataset$description)

```

```{r}
library(tidytext)
#Tokenizing
nasa_title <- nasa_title %>% 
  unnest_tokens(word, title) %>% 
  anti_join(stop_words)

nasa_desc <- nasa_desc %>% 
  unnest_tokens(word, desc) %>% 
  anti_join(stop_words)

#Removing custom stop words
my_stopwords <- data_frame(word = c(as.character(1:10), 
                                    "v1", "v03", "l2", "l3", "l4", "v5.2.0", 
                                    "v003", "v004", "v005", "v006", "v7"))
nasa_title <- nasa_title %>% 
  anti_join(my_stopwords)
nasa_desc <- nasa_desc %>% 
  anti_join(my_stopwords)

#Upper case to harmonize
nasa_keyword <- nasa_keyword %>% 
  mutate(keyword = toupper(keyword))
```

##Word co-occurence and correlations
```{r}
library(widyr)
#Count pariwise occurence in the title
title_word_pairs <- nasa_title %>% 
  pairwise_count(word, id, sort = TRUE, upper = FALSE)

title_word_pairs
```


```{r}
keyword_cors <- nasa_keyword %>% 
  group_by(keyword) %>%
  filter(n() >= 50) %>%
  pairwise_cor(keyword, id, sort = TRUE, upper = FALSE)

keyword_cors
```

##Calculating tf-idf
```{r}
desc_tf_idf <- nasa_desc %>% 
  count(id, word, sort = TRUE) %>%
  ungroup() %>%
  bind_tf_idf(word, id, n)

desc_tf_idf %>% 
  arrange(-tf_idf)

nasa_keyword <- data_frame(id = metadata$dataset$`_id`$`$oid`, 
                           keyword = metadata$dataset$keyword) %>%
  #Using nest because it is a list-column
  unnest(keyword)

desc_tf_idf <- full_join(desc_tf_idf, nasa_keyword, by = "id")
```

##Topic modeling

```{r}
my_stop_words <- bind_rows(stop_words, 
                           data_frame(word = c("nbsp", "amp", "gt", "lt",
                                               "timesnewromanpsmt", "font",
                                               "td", "li", "br", "tr", "quot",
                                               "st", "img", "src", "strong",
                                               "http", "file", "files",
                                               as.character(1:12)), 
                                      lexicon = rep("custom", 30)))

word_counts <- nasa_desc %>%
  anti_join(my_stop_words) %>%
  count(id, word, sort = TRUE) %>%
  ungroup()

#Dataset to document term matrix
desc_dtm <- word_counts %>%
  cast_dtm(id, word, n)

desc_dtm
```

```{r}
#Topic modeling
library(topicmodels)

# be aware that running this model is time intensive
desc_lda <- LDA(desc_dtm, k = 24, control = list(seed = 1234))
desc_lda
```

#Analyzing usenet text

```{r}
library(dplyr)
library(tidyr)
library(purrr)
library(readr)
```
##Pre-processing

```{r}
#Import des donnees
training_folder <- "TextMiningData/20news-bydate-train/"

# Define a function to read all files from a folder into a data frame
read_folder <- function(infolder) {
  data_frame(file = dir(infolder, full.names = TRUE)) %>%
    mutate(text = map(file, read_lines)) %>%
    transmute(id = basename(file), text) %>%
    unnest(text)
}

# Use unnest() and map() to apply read_folder to each subfolder
raw_text <- data_frame(folder = dir(training_folder, full.names = TRUE)) %>%
  unnest(map(folder, read_folder)) %>%
  transmute(newsgroup = basename(folder), id, text)
```

```{r}
library(ggplot2)

raw_text %>%
  group_by(newsgroup) %>%
  summarize(messages = n_distinct(id)) %>%
  ggplot(aes(newsgroup, messages)) +
  geom_col() +
  coord_flip()
```

```{r}
library(stringr)

# must occur after the first occurrence of an empty line,
# and before the first occurrence of a line starting with --
cleaned_text <- raw_text %>%
  group_by(newsgroup, id) %>%
  filter(cumsum(text == "") > 0,
         cumsum(str_detect(text, "^--")) == 0) %>%
  ungroup()

cleaned_text <- cleaned_text %>%
  filter(str_detect(text, "^[^>]+[A-Za-z\\d]") | text == "",
         !str_detect(text, "writes(:|\\.\\.\\.)$"),
         !str_detect(text, "^In article <"),
         !id %in% c(9704, 9985))

library(tidytext)
#Removing stop_words
usenet_words <- cleaned_text %>%
  unnest_tokens(word, text) %>%
  filter(str_detect(word, "[a-z']$"),
         !word %in% stop_words$word)
```

